Self-tunable approximated explicit MPC: Heat exchanger implementation and analysis

### 2023-07-25 paper/JoPC/main.tex
Paper: update

As the controlled system is naturally stable even if the maximal or minimal value of the manipulated variable is constantly applied, the constraints on the controlled variable in Eq.~\eqref{eq:mpc_problem_state_constraints} could be omitted. On the other hand, unbounded states/outputs lead to higher memory consumption, because covering the whole possible range of parameters requires more critical regions. Therefore, the "artificial" constraints on the outputs were included in order to reduce the number of critical regions and the overall memory footprint of the explicit controllers. The output constraints were set as: 
\begin{eqnarray}
	\label{eq:y_const}
	-15\,^{\circ}\mathrm{C} \le y \le 20\,^{\circ}\mathrm{C}.
\end{eqnarray}

@@

The explicit MPC corresponding to the penalty matrix $Q_\mathrm{y, U}$ contains 1\,680 critical regions, and the explicit MPC with the penalty matrix $Q_\mathrm{y, L}$ contains 409 critical regions. The corresponding polytopic partitions can be seen in Fig.~\ref{fig:partition_U} for the upper boundary controller and Fig.~\ref{fig:partition_L} for the lower boundary controller. To store the parametric solution associated with the upper boundary explicit MPC, 17.49 MB of memory space is required. Storing the lower boundary explicit MPC, one needs 4.33 MB of memory space.

>>>>

As the controlled system is naturally stable even if the maximal or minimal value of the manipulated variable is constantly applied, the constraints on the controlled variable in Eq.~\eqref{eq:mpc_problem_state_constraints} could be omitted. On the other hand, unbounded states/outputs lead to higher memory consumption, because covering the whole possible range of parameters requires more critical regions. Therefore, the ``redundant'' constraints on the system outputs were included in order to reduce the number of critical regions and the overall memory footprint of the explicit controllers. The output constraints were set as: 
\begin{eqnarray}
	\label{eq:y_const}
	-15\,^{\circ}\mathrm{C} \le y \le 20\,^{\circ}\mathrm{C}.
\end{eqnarray}

@@

The explicit MPC corresponding to the penalty matrix $Q_\mathrm{y, U}$ contains 1\,680 critical regions, and the explicit MPC with the penalty matrix $Q_\mathrm{y, L}$ contains 409 critical regions. The corresponding polytopic partitions can be seen in Figure~\ref{fig:partition_U} for the upper boundary controller and Figure~\ref{fig:partition_L} for the lower boundary controller. To store the parametric solution associated with the upper boundary explicit MPC, 17.49\,MB of memory space is required. Storing the lower boundary explicit MPC, one needs 4.33\,MB of memory space.
